---
title: "Happiness Levels"
author: "Kunal, Drew, Samiira, Diego"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Dynamic Paragraph
```{r summary, echo=FALSE, message=FALSE, include=FALSE}
source("../source/Summary_info.R")
all_sums <- get_relevant_summaries()
```

To summarize the information gathered from the data, we spread it out into different components that could influence what makes people happy. In our chart #1, we can see that based on region, North America and Western Europe are the places with the highest mean happiness score with a score above 'r all_sums$GDP_happiness_info$max' pictured in a lighter green. A perfect example is chart #2 which visualizes the effect of GDP, arguing the idea of money buying happiness. The hypothesis proved to be correct to a certain extent. With the following values. 
 -GDP_happiness_info<- list()
	-GDP <- happiness$`GDP per capita`
	-GDP_happiness_info$GDP_median <- median(GDP,na.rm = T)
	-GDP_happiness_info$GDP_max <- max(GDP,na.rm = T)
	-GDP_happiness_info$GDP_min <- min(GDP,na.rm = T) 

The data on the plot shows that there isn't a single country with a GPA under 1.00 that ranks above 30th. On the other hand, many outliers disregard the importance of a country's wealth as a determinant of their happiness. For example, Kuwait has a GDP of 1.474 and is ranked 45th compared to Brazil which has a GDP of 0.986 and is ranked 28th. Lastly, under the assumption that money is the main determinant of happiness. United Arab Emirates has the highest GDP in the data but is only ranked 20th. Lastly, our 3rd Chart shows us the top ten happiest countries and their score. Finland is at #1 with a score of 7.632 and so on Australia is at #10 with 7.272. To understand the data and variables such as year, social support, health/ life expectancy, and generosity we grouped them by the percentage of the two years of the data. For example, we have in our data the mean of 0.789 a maximum of 1.141 & a minimum of 0 for life expectancy/health. To compare them to where they ranked on the happiness index and evaluate their importance. Identifying the trends that prove to have the strongest correlation to the changes in the rankings.




## Aggregate Table
```{r agg_table, echo=FALSE, message=FALSE}
source("../source/aggregate_operations.R")
kable(display_grouped_averages())
```

This table depicts the means of happiness score, social support, life expectancy, and generosity ratings, grouped by each year. This table reveals interesting information because while happiness mean does not show a trend increase from 2018 to 2019, life expectancy noticeably increased. It’s important to remember that causation does not mean correlation—life expectancy could have increased for reasons other than happiness. Because of this, I think it is fair to say that in general, world happiness and the related metrics did not increase substantially from 2018 to 2019.


## Charts
```{r chart1, echo=FALSE, message=FALSE, warning=FALSE}
source("../source/chart1.r")
world_happiness_plot()
```

Chart 1 is meant to show which regions of the world are the happiest. 
People in North America and Western Europe appear to be the happiest.
This chart was included for a visualization of where people are the least and most happy.


```{r chart2, echo=FALSE, message=FALSE}
source("../source/chart2.R")
gdp_happiness_scatplot()
```

Chart 2 depicts the relationship between GDP per capita and happiness.
This chart was included to test the popular phrase "Money can't buy happiness".
This chart reveals that increases in GDP per capita does improve the overall happiness of a country. However, there are large variances, where some countries have nearly the same GDP per capita but have large disparities in happiness.


```{r chart3, echo=FALSE, message=FALSE}
source("../source/chart3.r")
happiness_top_ten()
```

Chart 3 shows the happiest places in the world. 
The Scandinavian countries appear to be the happiest.
This chart was included to highlight the countries with the highest happiness ratings.



